ANGSD-wrapper: utilities for analyzing next generation sequencing data

### 2016-01-29 manuscript.tex
oh thats what jeff meant

\begin{figure}
\centering
\includegraphics[width=0.8\linewidth]{figures/figure3big.pdf}
\caption{Summary statistics for {\it Zea mays}. Derived site frequency spectra for A. maize and B. teosinte. C. distribution of pairwise nucleotide diversity for maize (blue) and teosinte (orange). Pairwise nucleotide diversity results are visualized separately from the interactive graphics and colors were added to A and B using a custom script.}
\label{fig:figure3}
\end{figure}

@@

We first use the ``SFS'' method to estimate the site frequency spectrum (SFS) of both maize and its wild progenitor \textit{Zea mays} ssp. \textit{parviglumis}, assuming an inbreeding coefficient of $F=1$ for these highly inbred samples. 
The SFS and diversity statistics were calculated using ancestral states inferred in the ``Ancestral Sequence'' method from a single resequenced genome of \textit{Tripsacum dactyloides}.  
We show that the maize SFS is skewed towards more intermediate-frequency variants (Figure \ref{fig:figure3}A-B, Tajima's D of 0.2 and 0.0085 in maize and teosinte, respectively), likely a result of the bottleneck associated with maize domestication \citep{eyre1998investigation, Beissinger031666}.
Using the ``Thetas'' method we find further evidence of the domestication bottleneck, with mean levels of pairwise nucleotide diversity in this region in maize $\approx 25\%$ lower than in teosinte (0.0061 and 0.0082, respectively). Figure \ref{fig:figure3}C shows the distribution of pairwise nucleotide diversity in each window within our region of interest and each vertical line represents the number of windows with the corresponding value of $\pi$. 
Using the ``2DSFS method,'' which includes an \fst calculation, we find a mean \fst in this region of 0.116, nearly identical to the  genome-wide value of 0.11 reported in \cite{hufford2012comparative}.   
There are no genes in this region that have  been identified as potential domestication candidates, consistent with the lack of extended regions of high \fst in our analysis (Figure \ref{fig:suppfst}).

>>>>

\begin{figure}
\centering
\includegraphics[width=0.8\linewidth]{figures/figure3big.pdf}
\caption{Summary statistics for {\it Zea mays}. Derived site frequency spectra for A. maize and B. teosinte. C. distribution of pairwise nucleotide diversity for maize (blue) and teosinte (orange). Mean values for each taxa are represented by corresponding vertical lines. Pairwise nucleotide diversity results are visualized separately from the interactive graphics and colors were added to A and B using a custom script.}
\label{fig:figure3}
\end{figure}

@@

We first use the ``SFS'' method to estimate the site frequency spectrum (SFS) of both maize and its wild progenitor \textit{Zea mays} ssp. \textit{parviglumis}, assuming an inbreeding coefficient of $F=1$ for these highly inbred samples. 
The SFS and diversity statistics were calculated using ancestral states inferred in the ``Ancestral Sequence'' method from a single resequenced genome of \textit{Tripsacum dactyloides}.  
We show that the maize SFS is skewed towards more intermediate-frequency variants (Figure \ref{fig:figure3}A-B, Tajima's D of 0.2 and 0.0085 in maize and teosinte, respectively), likely a result of the bottleneck associated with maize domestication \citep{eyre1998investigation, Beissinger031666}.
Using the ``Thetas'' method we find further evidence of the domestication bottleneck, with mean levels of pairwise nucleotide diversity in this region in maize $\approx 25\%$ lower than in teosinte (0.0061 and 0.0082, respectively; Figure \ref{fig:figure3}C). 
Using the ``2DSFS method,'' which includes an \fst calculation, we find a mean \fst in this region of 0.116, nearly identical to the  genome-wide value of 0.11 reported in \cite{hufford2012comparative}.   
There are no genes in this region that have  been identified as potential domestication candidates, consistent with the lack of extended regions of high \fst in our analysis (Figure \ref{fig:suppfst}).
